D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-05-12 doc/article/article.tex
Draft

\begin{table}[htbp]
\caption{Text Distance Metrics}
\centering
\begin{tabular}{lccc}
\hline
\textbf{Model} & \textbf{Hamming} & \textbf{Cosine} & \textbf{Euclidean} \\
\hline
microsoft-trocr-small-printed & 1.392 & 0.150 & 7133 \\
microsoft-trocr-base-printed & 1.286 & 0.081 & 3594 \\
microsoft-trocr-small-handwritten & 1.346 & 0.100  & 3947 \\
microsoft-trocr-base-handwritten & --- & --- & --- \\
% Add more models as needed
\hline
\end{tabular}
\label{tab:text_digitization}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Text Distance Metrics}
\centering
\begin{tabular}{lccc}
\hline
\textbf{Model} & \textbf{Hamming} & \textbf{Cosine} & \textbf{Euclidean} \\
\hline
microsoft-trocr-small-printed & 1.392 & 0.150 & 7133 \\
% microsoft-trocr-base-printed & 1.286 & 0.081 & 3594 \\
microsoft-trocr-small-handwritten & 1.346 & 0.100  & 3947 \\
microsoft-trocr-base-handwritten & 1.549 & 0.057 & 3003 \\
\hline
\end{tabular}
\label{tab:text_digitization}
\end{table}

Some examples of the different models applied to our graph diagram dataset can be seen in Figure~\ref{fig:text_digitization_results_1}.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{text_digitization_results_1.png}
\caption{Some random results of the text digitization over the proposed models.}
\label{fig:text_digitization_results_1}
\end{figure}
